% Reading and Writing Data
% Weicheng Zhu
% 2012/06/04

  <font size = 3 color = "blue">Highly recommend you to use Chrome to read this tutorial! <br /> This tutorial is mainly for Windows users.</font>
-----------------------------------------------------------------------
```{r setup, include=FALSE}
# set global chunk options
opts_chunk$set(fig.path = 'figure/slides-', cache.path = 'cache/slides-', cache = TRUE)
#options(width = 55)
#options(keep.comment = FALSE) 
#upload images automatically
#opts_knit$set(upload.fun = imgur_upload)
```

```{r code-ext, include = FALSE, cache = FALSE}
read_chunk('Rclass4.R')
```

# Saving and Loading R Objects

## `save` and `save.image`

- Description
    - `save()` writes an external representation of R objects to the specified file.
    - `save.image()` is just a short-cut for 'save my current workspace', i.e., `save(list = ls(all=TRUE), file = ".RData")`.    
- Feature
    - Efficient: The data is saved in (compressed) binary form
    - For short-term storage: Binary formats are usually not possible to recovery if they are corrupted.
    
- Examples

```{r save}

```

## `load`

- Description
    - Reload datasets written with the function `save`.

- Examples

```{r load}

```

- More
    - When you start R, R will automatically load the `.RData` file if it exits in your default working directory.


# A break: Working Directory

- `getwd()` returns an absolute filepath representing the current working directory of the R process; 
- `setwd(dir)` is used to set the working directory to `dir`.
- Examples

```{r  working-directory}

```

- [How to set the working directory in R permanently?][working-directory]

# Reading and Writing External Files

## `read.table()` function

- Description
  The `read.table` function is one of the most commonly used functions for reading data. It reads a file in table format and creates a data frame from it, a few important arguments is listed as follows:

    - `file`, the name of a file, or a connection
    - `header`, logical indicating whether the file contains the names of the variables as its first line
    - `sep`, a string indicating how the columns are separated. If `sep = ""` the separator is 'white space'
    - `na.strings`, a character vector of strings which are to be interpreted as NA values.
    - `colClasses`, a character vector indicating the class of each
      column in the dataset
    - `nrows`, integer: the maximum number of rows to read in
    - `skip`, the number of lines to skip from the beginning
    - `stringsAsFactors`, logical: should character vectors be converted to factors?

- `read.table` family
  R includes a set of convenience functions that call `read.table` with different default options for these values (and a couple of others). Here is a description of these functions


Function       header      sep      quote    dec     fill                comment.char
------------  ----------  ------  --------  ------ ------------------- --------------
read.table     FALSE               " or '    .      !blank.lines.skip     #
read.csv       TRUE        ,          "      .      TRUE
read.csv2      TRUE        ;          "      ,      TRUE
read.delim     TRUE       \\t          "      .      TRUE
read.delim2    TRUE       \\t          "      ,      TRUE


- Some useful tips:

    - Reading data set by URL
    - Reading data set from the "clipboard"
    - Take advantage of the `file.choose()` function
    - For larger datasets, specifying `colClasses` argument can make `read.table` run much faster.

- Examples:

```{r readtable, eval=FALSE}

```

## `write.table()` function

- Description
  Opposite to `read.table()` function, used to print dataframe or matrix to file or connection.

- Examples

```{r writetable, eval=FALSE}

```

## `dput` and `dget`

- Description
  Writes an ASCII text representation of an R object to a file or connection, or uses one to recreate the object.

- Feature
    - Only one object can be written
    - The object name is not written
    - The associated environment of the function to be written is stripped. Hence scoping information can be lost.
    - It's really a good habit to use `dput` function to generate reproducible problems when asking questions related to R.
    
- Examples

```{r dput-dget, eval=FALSE}

```

## `dump`

- Description
  This function takes a vector of names of R objects and produces text representations of the objects on a file or connection. 

- Feature
    - One or more R objects can be dumped
    - The object names are written
    - Usually you can use `source` function to read the `dump` file
    
- Examples

```{r dump, eval=FALSE}

```


## `source`

- Description
  `source` causes R to accept its input from the named file or URL or connection.
  
- Feature
    -  `auto-printing` is not done, so you will need to include explicit `print` calls for things you want to be printed (and remember that this includes plotting by `lattice`
    - The complete file is parsed before any of it is run, syntax errors result in none of the code being run.
    
- Examples

```{r source, eval = FALSE}

```

## Others

- `readLines`, `writeLines`
- `cat`, `scan`
- `readChar`, `writeChar`
- `write`
- `connection`
- package: `xlsx`
  
- Examples

```{r others, eval=FALSE}

```














[working-directory]: http://dreamhunter.me/bbpress/Rstudy/working-directory.html














