% Middle level R: S3 methods
% Weicheng Zhu
% 2012/05/24

  <font size = 3 color = "blue">Highly recommend you to use Chrome to read this tutorial! <br /> This tutorial is mainly for Windows users.</font>
-----------------------------------------------------------------------
```{r setup, include=FALSE}
# set global chunk options
opts_chunk$set(fig.path = 'figure/slides-', cache.path = 'cache/slides-', cache = TRUE)
#options(width = 55)
#options(keep.comment = FALSE) 
#upload images automatically
opts_knit$set(upload.fun = imgur_upload)
```

```{r code-ext, include = FALSE, cache = FALSE}
read_chunk('Rclass3.R')
```

# S3 Methods

## Review

To start with, let's have a look at a simple code:


```{r startwith}
```

**Have you ever been curious about HOW `print` function recognize the objects to be printed?**

**And have you ever been curious about HOW `summary` function work with the returned value (`res`) of the `lm` function?**

To solve these problems you should learn **methods** of R.

## What is it?

There are two types of methods in R, *S3* methods and *S4* methods.

- *S3* methods
  - Included with version 3 of the *S* language.
  - Informal but more convenient
  - Sometimes called *old-style* methods
  - packages: most of R??s own built-in classes are of the *S3* type
- *S4* methods
  - more formal and safe
  - Included with *S-PLUS 6, R 1.4.0*
  - Also called *new-style* methods
  - packages: stats4, SparseM, gpclib, flexmix, its, lme4, orientlib, pixmap

## Which to use?

In fact, to use which kind of methods depends on your personal choice of which you value more -- the convenience of *S3* or the safety of *S4*.

In this document I'll ONLY introduce *S3* methods, because it is easier to learn both for the syntax and the concepts.


## Dig up the `print` function

"Stand up from where you tripped over!" -- so, Let's go into `print` function.

First of all, let's have a look at the code of the `print` function:

```{r print-fun}
print
```

WOW, ONLY ONE LINE CODE! How R does this magic?

In fact, the code you see is a 'fake' one. The `print` function is just a dispatcher function, the so called *generic function*.

You can define a generic name for a set of functions (like `fun`). When you call `fun` on an object, R will find the correct method to execute based on the class of the object.

Let's have a look indeed what happened when we call `print(res)` in the previous example.

First, when we call `print` function, it will check the class of the object.

```{r print-class}
class(res)
```

Then, `print` function will try to find whether there is a method called `print.lm`.

```{r printlm}
print.lm
```

Fortunately, there is a function called `print.lm`, so `print.lm` function will be used to print the object with a `lm` class. So if you use `print.lm(res)`, you'll get the same results.

Similarly, let's check that for `print(x)`.

First, check the class of `x`.

```{r x-class}
class(x)
```

Then, check whether there is a function called `lm.numeric`.

```{r}
lm.numeric
```


But unfortunately this time, there is no print method defined with the class of `numeric`. In this case, `print.default` will be called. You can use `print.default(x)` to check it.


## Sum up

In general the first argument of a generic function is an object of a particular class

1. The generic function checks the class of the object.
2. A search is done to see if there is an appropriate method for
that class.
3. If there exists a method for that class, then that method is
called on the object and we’re done.
4. If a method for that class does not exist, a search is done to
see if there is a default method for the generic. If a default
exists, then the default method is called.
5. If a default method doesn’t exist, then an error is thrown.

## Create generic function using *S3*

1. Pick a name for the generic function, say "`myfunction`".
2. Create a function named `myfunction`. In the body for `myfunction`, call `UseMethod("myfunction")`.
3. For each class that you want to use with `myfunction`, create a function called `myfunction.classname` whose first argument is an object of class `classname`.

## Other tips

OK, I know you can't wait to try your first generic function, but before doing that I'll tell some more tips.

- `methods(generic.function, class)`
  List all available methods for an *S3* generic function, or all methods for a class. 
  
```{r methods, eval = FALSE}
methods(print)
methods(summary)
methods(class="default")
```

- `getAnywhere(x)`
  Of all the implementations of a given generic method, asterisks denote nonvisible functions, meaning ones that are not in the default namespaces. In this case you can use `getAnywhere(functionname)` to display the code.
  
  
```{r getanywhere, eval = FALSE}
getAnywhere(summary.loess)
getAnywhere(print.summary.loess)
```

- `getS3method(f, class, optional = FALSE)`
  Similar with `getAnywhere`

```{r gets3method, eval=FALSE}
getS3method("summary", "loess")
```
- `:: and :::`
  Similar with `getAnywhere`
  
  
  
```{r dblcolon, eval=FALSE}
base::log
stats:::coef.default
```


## Write your own methods!

- Why?
    - To represent new types of data (e.g. gene expression, space-time, hierarchical, sparse matrices)
    - New concepts/ideas that R does not know about them (e.g. a fitted point process model, mixed-effects models)
    - To abstract implementation details from the user

- If you write new methods for new classes, you??ll probably end up writing methods for the following generics:

    - `print`
    - `summary`
    - `plot`


- Exercise1: create a function called `ratio` to get the following results:

```{r methods1, include=FALSE}

```

```{r methods1-res}
ratio(3, 4)
```

- Exercise2: update `ratio` to get the following effect:

```{r methods3, include=FALSE}

```

```{r method3-res}
ratio(3, 4)
ratio(19, 30)
ratio(100, 1000)
```

## `NextMethod`

It's too complex to express in words, so let's directly see an example:

```{r nextmethod}

```












