% R Graphics
% Weicheng Zhu
% 2012/06/06

  <font size = 3 color = "blue">Highly recommend you to use Chrome to read this tutorial! <br /> This tutorial is mainly for Windows users.</font>
-----------------------------------------------------------------------
```{r setup, include=FALSE}
# set global chunk options
opts_chunk$set(fig.path = 'figure/slides-', cache.path = 'cache/slides-', cache = TRUE)
#options(width = 55)
#options(keep.comment = FALSE) 
#upload images automatically
#opts_knit$set(upload.fun = imgur_upload)
```

```{r code-ext, include = FALSE, cache = FALSE}
read_chunk('Rclass5.R')
```

# Outline

## Examples

Now we are going to one of the most attractive part of R language: **Graphics**.
First, before we actually go into it, let's enjoy the view of R graphics together :)
The purpose here is just to make you have an overall impression of the range of graphical images that can produced by R :)

```{r review}

```

To see more at the [R Graph Gallery][gallery]

## Organization

- Graphics Systems
  There are two big graphics systems in R, `traditional graphics` and `grid`.

- Graphics Devices (package)
  Default (`grDevices`),  Cairo/GTK (`cairoDevice`), SVG (`RSvgDevice`), Java (`JavaGD`), OpenGL (`rgl`), Gtk (`RGtk2`)

- Graphics Packages
    - `graphics` (traditional graphics system)
    - `lattice`, `ggplot2` (grid system)
    - ...

- I'll omit all details here, and turn back if necessary later. For more information, see [http://cran.r-project.org/web/views/Graphics.html](http://cran.r-project.org/web/views/Graphics.html)

# Traditional Graphics

We'll cover most of the functions in `graphics` package in this section.

To begin with, let's have a look at the most usually used function `plot()`.

## `plot()` function

Recall that `plot()` is a [generic function][generic-function], so it can accept objects from a variety of [classes][attribute]. But many methods will accept the following arguments:
- `x`: coordinates OR function OR R object with a plot method can be provided.
- `y`: y coordinates OR optional if x is an appropriate structure.
- `type`: what type of plot should be drawn. Possible types are `"p", "l", "b", "c", "o", "h", "s", "S", "n"`
- main: an overall title for the plot
- sub: a sub title for the plot
- xlab: a title for the x axis
- ylab: YOU KNOW
- asp: the y/x aspect ratio

Also we can check the arguments of the `plot.default()` function, we can note it has more arguments, I won't explain more arguments here, but notice the defination of `x` and `y` here, they are different from the `plot()` function's. I hope you can understand the underlying mechanism, if not please read [S3 methods][generic-function] carefully.
Let's study these arguments through some examples.

### `type`

```{r plot-type}

```

### `pch`

```{r plot-pch}

```

## *High-level* Functions
Generally speaking, a *High-level* plotting function is a function that can be used to produce a complete plot by itself. Let's have a look at some of the most usually used high-level functions through the following examples:

```{r high-level}

```

## *Low-level* Functions
It is very often the case that a high-level plotting function does not produce exactly the final result that is desired. In this case, we should use low-level functions to control the fine details of a plot. Also let's have a look at some of the low-level functions through examples:

```{r low-level}

```







[gallery]: http://addictedtor.free.fr/graphiques
[generic-function]: http://dreamhunter.me/bbpress/Rstudy/Rclass3.html
[attribute]: http://dreamhunter.me/bbpress/Rstudy/attributes.html











