Basic R: Introduction and basic functions
=========================================

[Weicheng Zhu](http://dreamhunter.me)

2013/04/30

```{r, setup-options ,cache=FALSE, echo=FALSE}
read_chunk('./Rcode/part01_practice.R')
opts_chunk$set(cache=FALSE, eval=FALSE)
```

## Why R
- Free!
- Open Source!
- Command line: flexible
- Advanced (newest) statistical routines (4391 packages available now)
- Runs on a wide variety of platforms: Windos, UNIX,  MacOS...
- Access to database: Oracle, DB2, MySQL...
- Foreign language interfaces: C, C++, Fortran, Python, Java...
- Other statistical software can invoke R codes
- Dynamic report generation: R + LaTeX (`knitr`, `Sweave`)
- ...

## Downloading and Installing R
- Download it from [CRAN][cran]
	- CRAN?
	- mirrors?
- Install: (In Windows) click, click, click...
- Other popular GUIs: Rstudio, Tinn-R, RKward, Notepad++, Emacs, Vim, ...

# Working with R

- Prompts: 
	- `>`, `+`: change it via `options(prompt = "", continue = "")`
- Comments
  - `#`
- Basic Operation
	- Math operator: `+`, `-`, `*`, `/`, `^`, `%%`, `%/%`
	- logical operator: `&`, `&&`, `|`, `||`, `!`, `>`, `<`, `>=`, `<=`, `==` <font color = "red">(difference between `&` and `&&`?)</font>
- Basic math functions
	- `sqrt()`, `sin()`, `cos()`, `tan()`, `abs()`, `log()`, `exp()`, `factorial()`, `choose()`


## Variables

- Assignment operator: `<-`,`=`, `assign`

```{r}
x <- 1; y = FALSE; assign("z", pi)
k <- x + y + z > 0
```

- Case sensitive

- Reserved words

```{r,tidy=FALSE}
?Reserved
```

## Data types
- `numeric(real, integer, double)`, `complex`, `logical`, `character`, `function`, `expression`, ...
`?mode`

- `NULL` (no value), `NA` (Not Available), `NaN` (Not a Number), `Inf` (Infinity) 

- Judge Data types (add `is.` prefix to the data types)

```{r}
is.numeric(); is.logical(); is.character(); is.na(); is.nan(); is.null(); ...
```

- Transfer Data types (add `as.` prefix to the data types)

```{r}
as.numeric(); as.logical(); as.character(); ...
```

## Data structures

- vector: We can TREAT IT AS a column vector with numeric, character or logical type elements. 
- matrix: Two dimensions, all elements should have the same data type.
- array: Multi dimensions, all elements should have the same data type.
- data frame: Similar with matrix, but every column can have different data types.
- list: Like an expanded vector, whose elements can be any type, even list itself.
- factor: A categorical vector.
- ts: Time series data.

### vector

```{r, vector}
```

### factor

```{r, factor}
```

### matrix

```{r, matrix}
```

### array

```{r, array}
```

### dataframe

```{r, dataframe}
```

### list

```{r, list}
```


### Data structure judgement

```{r}
is.vector()
is.data.frame()
is.matrix()
is.list()
is.factor()
is.ts()
```

### Data structure transformation

```{r}
as.data.frame()
as.matrix()
as.list()
as.factor()
as.ts()
unlist() # transform list to vector
```

## Basic calculation

- vector + constant

```{r}
vec1 + 1
```

- vector + vector

```{r}
vec1 + vec2
```

- vector * constant

```{r}
2 * vec1
```

- vector / constant

```{r}
vec1 / 2
5 / vec1
```

- vector * vector

```{r}
vec1 * vec1
```

- vector * matrix

```{r}
mat4 * vec1 # equivalent to vec1 * mat4
```

- *vector %\*% matrix*

```{r}
t(vec1) %*% mat4
vec1 %*% mat4
vec1 %*% vec1
t(vec1) %*% vec1
vec1 %*% t(vec1)
```

- matrix * matrix

```{r}
mat4 * mat4
mat4^2
```

- matrix %*% matrix

```{r}
mat4 %*% t(mat4)
```

## Functions

- `f(argument1, argument2, ...)`
- Basic statistical functions

```{r}
sum(); mean(); max(); min(); range(); var();
sd(); median(); quantile();	cor(); length();
round(); floor(); ceiling(); summary()
```

```{r}
sort(); order(); rank(); rev(); cusum(); 
t(); solve(); eigen()
```

```{r}
pnorm(); dnorm(); qnorm(); rnorm()
```

p: probability; d: density;
q: quantile; r: random\
For more, see: `?Distributions`

```{r}
lm(); t.test(); aov()
```

## <font color = "red">HELP!!</font>

### The structure of the help documents
- `?foo` OR `help(foo)`
- function name {package	}
- Title
- Description: what can the function do?
- Usage: the format of the function
- Arguments: details about the arguments
- Details: details about the function
- Value: what value does the function return?
- References
- See Also: related functions
- Examples: examples about this function

### How to read help?
- First, read the *Description* carefully
- If you are in a hurry, go to the *Examples* directly
- Usually, after running the *Examples* you may have known the usage of the function in general
- If not, read the arguments carefully
- If you still can't understand the function (or the arguments) well, read the *Details* part
- If after reading all of this above, you still can't solve your problem, you may get the wrong function, try others.

### If you don't know which function to use
- The best way is to GOOGLE! You should use the keywords: R + what you want to search.
- `?help.search()`
- `help.start()`
- `RSiteSearch()`
- `apropos()`


# Appendix

## Usefull keybindings
- In R console
	- `Ctrl + a`
	- `Ctrl + e`
	- `Ctrl + f`
	- `Ctrl + b`
	- `Ctrl + p`
	- `Ctrl + n`
	- `Ctrl + d`
	- `Ctrl + k`
	- `Ctrl + l`
- In R editor
	- `Ctrl + r`


[habit]:http://google-styleguide.googlecode.com/svn/trunk/google-r-style.html
[book4R]:http://www.r-project.org/doc/bib/R-publications.html
[UseR]:http://www.springer.com/series/6991?detailsPage=titles
[cran]:http://cran.r-project.org/mirrors.html